% Single spacing can be turned on for the abstract
%
{
	
	\singlespacing \noindent
	This thesis details the development of machine learning techniques for the benefit of safety analysis in the UK nuclear energy sector. The objective of this research was to develop machine learning models which can perform the same functionality as existing industry standard models but with reduced computational intensity.  
	
	\singlespacing \noindent
	The UK nuclear industry is dominated by the advanced-gas cooled reactor (AGR), a design which differs considerably to most reactors elsewhere in the world. As a result of its novelty, there is a lack of international research to draw on concerning operation and safety. The situation is further complicated by the complexity of AGR safety analysis, involving thousands of different components in various scenarios and configurations. Therefore, AGR safety analysis and research is computationally intensive whilst being highly time sensitive.
	
	\singlespacing \noindent
	A key research objective was the production of surrogate machine learning (SML) models. These models are produced intention of retaining the functionality of an existing model i.e. it produces similar outputs from the same inputs whilst reducing computational cost.
	
	\singlespacing \noindent
	Through the development of SMLs for this research work, two articles were written and published in peer-reviewed academic journals. The first details the generation and preparation of data, as well as the process of developing an SML for our purpose. The second article details improvements to the method outlined in the first article. 
	


}

